---
title: "Alexandria Coombe Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
```

## Intro {.sidebar}

DACSS 604
Assignment Four

You can find the code for the plot & map here:
https://github.com/ACC-UMASS/FinalProject-690V

## Column {.tabset .tabset-fade}

### Univariate Categorical Plot

```{r}
readRDS("liberalization2020PercentFinal.RDS")
```

Status of cannabis laws for the year 2020. 

### Choropleth Map

```{r}
readRDS("mapFinal.RDS")
```

This map shows the crime rates per 100,000 residents in all fifty states for the year 2020. 

### References

I created the cannabisData2020 dataset that was utilized for these plots. The data was collected from the following sources:

* FBI Uniform Crime Reporting program
* The FBI Crime Data Explorer 
* The United States Department of Justice 
* The Drug Enforcement Administration
* Each state’s government website
* The Federal Bureau of Prisons
